Generality in food webs scales with species richness but not with latitude

### 2015-06-18 manuscript/latitudepaper.tex
updated supplement and fixed parentheses in coverletter

\vspace{0.3 in}

@@

Several properties of food webs---the networks of feeding links between
species---vary systematically with the species richness of the underlying
community.  Under the ``latitude-niche breadth hypothesis'', which predicts
that species in the tropics will tend to evolve narrower niches, one might
expect that these scaling relationships could also be affected by latitude. To
test this hypothesis, we analysed the scaling relationships between species
richness and average generality, vulnerability, and links per species across a
set of 163 empirical food webs.  We also investigated scaling relationships
between the three food-web properties and the proportions of the web made up
by basal resources, intermediate consumers, and top predators. While we
observed no effect of latitude on scaling relationships in the estuarine,
marine, and terrestrial food webs, there were strong effects of latitude on
scaling relationships in the freshwater food webs. In these communities, the
latitude-niche breadth hypothesis appears to hold true while in other habitat
types niches appear to be broader in the tropics. These contrasting findings
indicate that it may be more important to account for habitat than latitude
when exploring gradients in food-web structure.

@@

  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
  Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
  ecological communities~\citep{Petchey2008,Williams2000,Paine1966} and to understand how that structure relates to environmental variables 
  such as habitat type~\citep{Shurin2006,Briand1983}, primary productivity~\citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate~\citep{Baiser2012,Petchey2010}. The latter
  variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
  climate is more variable at high latitudes~\citep{Field1998}. These variables affect both the resources available and species' 
  metabolisms~\citep{Hechinger2011,White2011,OConnor2009,White2007}, and have been proposed as determinants of the strength of 
  interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
  By modulating interactions between species, latitudinal gradients may also shape food-web structure.
  Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
  latitudinal gradient in species richness, one of the most general and robust patterns in ecology~\citep{Schemske2009a,Macpherson2002,Kaufman1995}.

@@

  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
  degree of specialization (i.e., niche breadth) of species within food webs.
  Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. 
  For example,
  narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{Dyer2007,Marra1997} but see~\citep{Schleuning2012}). However,
  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialization may be obscured by a latitudinal gradient in species richness. If this is
  the case, it may still be possible to uncover effects of latitude on specialization by examining the shape of the scaling 
  relationship between specialization and species richness over changing latitude. Here, we use three measures of specialization:
  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
  latitude affects the scaling of each property with species richness, we test effects of latitude on specialization implied by
  the ``latitude-niche breadth hypothesis''.

@@

    We compiled a list of 163 empirical food webs from
    multiple sources (see Supplemental Information for web origins and selection
    criteria). We recorded study site latitude from the original source where
    possible or, where study sites were described but exact coordinates were not
    given, obtained estimated coordinates using Google Earth~\citep{GoogleEarth}.
    We then divided the species in each web into basal resources (those species with
    consumers but no prey), top predators (those species with prey but no predators),
    and intermediate consumers (species with both predators and prey, including cannibalistic
    species).

    As the food webs in this dataset are derived from a variety of sources and were compiled over many decades, it
    is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
    Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
    sets to form ``trophic species'' webs (e.g.~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}). As this study
    is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
    species with redundant sets of interactions. We therefore analysed both original and trophic-species versions
    of the dataset; in each case using the number of species ($S$) and 
    links ($L$) in each web to calculate the mean number of links per species ($Z$), mean generality 
    ($G$), and mean vulnerability ($V$) of the web. 
    The version of the dataset used did not qualitatively change the results, suggesting that
    the scaling relationships between species richness, other food-web properties, and latitude are very 
    similar whether or not redundant species are included. For simplicity, we present only
    the results for the original webs.

  \subsection*{Relationships with Latitude}

    To determine whether there were latitudinal gradients in food-web structure,
    we first examined simple linear relationships between latitude and each of 
    species richness, links per species, generality, vulnerability, and proportions
    of basal resources, intermediate consumers, and top predators. We fit models of the form

    \begin{equation}
    \label{Latfull}
    S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
    \end{equation}

    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
    marine, lake, and terrestrial networks with estuarine
    networks providing the intercept) and $\epsilon_{i}$ a residual error term. 
    We next calculated the AIC
    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
    using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
    Simplified models were obtained by
    systematically removing all possible combinations of terms from the full model.
    The best-fitting model was then determined to be the model with the fewest terms 
    where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
    and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
    model.

@@

    Next, we examined the form of the scaling relationship between each 
    property (links per species, generality, and vulnerability) and 
    species richness. The scaling relationship between links per species ($Z$) and 
    species richness ($S$) has been shown to be a power law~\citep{Riede2010} of the form

@@

    \noindent Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
    Specifically, equation~(\ref{Power}) implies a normally-distributed, additive error and equation~(\ref{Loglog}) a lognormal,
    multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
    over another, we follow the recommendations in~\citet{Xiao2011} and compared the two
    model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
    data was then used to test for potential effects of latitude.

    Although scaling relationships between species richness and generality or
    species richness and vulnerability have not been explicitly examined (but see scaling 
    relationships for the standard devaitions of each property in~\citet{Riede2010}), we expect that they will follow
    power laws similar to that of the relationship between species richness and links per species.
    This is because the links taken into account in calculating generality and vulnerability are subsets 
    of the total links included when calculating links per species. As with links per species, we explicitly 
    compared the error distributions of models for generality and vulnerability using
    both the power-law and logarithmic formulations. 
    In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
    species richness.

@@

    We then assessed the impact of latitude on the scaling relationships between species richness and 
    link density, generality, vulnerability. In the context of the scaling relationships above, note 
    that this implies that we aim to determine the effect of latitude on
    the scaling exponent $\beta$. As when examining the relationships between latitude and each food 
    web property directly, we included a categorical variable for ecosystem type (stream, lake, 
    terrestrial, marine, or estuary), as well as interactions between food web type and latitude.

@@

  \subsection*{Relationships with Latitude}

    Contrary to the expected latitudinal gradient, the best-fit version of
    equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
    ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
    relationship was robust to the removal of three outliers (based on Cook's Distance). 
    There were also relationships between latitude and link density and latitude and vulnerability
    in stream food webs, but these trends were non-signficant after the removal of three outliers.
    Link density and vulnerability did not vary with latitude in any other ecosystem type.
    The best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
    latitude in any ecosystem type.

    The relationships between latitude and the proportions of species at each trophic level were broadly similar
    to the relationship between latitude and species richness. 
    The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.012, $p$\textless0.001) 
    but did not vary with latitude in estuarine, marine, lake, or terrestrial 
    food webs ($\beta_{Latitude}$=0.001, $p$=0.139).
    The proportion of intermediate consumers did not vary with latitude in any ecosystem type.
    The proportion of top predators did not vary with latitude in 
    estuarine, marine, or terrestrial food webs ($\beta_{Latitude}$=0.001, $p$=0.136) but decreased towards the poles in stream and lake food 
    webs ($\beta_{Latitude:Stream}$=-0.006, $p$=0.030; 
    $\beta_{Latitude:Lake}$=-0.006, $p$=0.001). 
    All of these trends were robust to the removal of outliers.

  \subsection*{Form of scaling relationships}

    When considering the relationships between species richness or the proportions 
    of basal resources, intermediate consumers, or top predators and all response variables 
    (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
    lower AIC than did equation~(\ref{Power}). This indicates that the
    data support an assumption of multiplicative lognormal error better than an
    assumption of additive normal error. That is, models where $\epsilon$ is
    modelled as an additive term on
    the logarithmic scale provide a better description of the data than models
    where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
    We therefore used logarithmic-form models when assessing the
    effect of latitude on scaling relationships  with species richness.

  \subsection*{Effect of Latitude on Scaling with S, B, I, and T}

    Link density, generality, and vulnerability each increased with increasing
    species richness (Fig.~\ref{S}; $\beta_0$=0.666, $p$\textless0.001; $\beta_0$=0.623,
    $p$\textless0.001; and $\beta_0$=0.666, $p$\textless0.001 respectively).  For estuarine,
    marine, and terrestrial food webs this increase did not vary with latitude
    ($\beta_{Latitude}$=-0.001, $p$=0.267 for link density; $\beta_{Latitude}$=-0.001, $p$=0.363 for generality;
    and $\beta_{Latitude}$=-0.001, $p$=0.267 for vulnerability). In lake food webs, link density,
    generality, and vulnerability all increased more quickly towards the poles
    ($\beta_{Latitude:Lake}$=0.005, $p$=0.008; $\beta_{Latitude:Lake}$=0.005,
    $p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively). In
    stream food webs generality increased more rapidly towards the poles 
    ($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability did not vary with latitude.

    In general, link density, generality, and vulnerability decreased as the
    proportion of basal resources in a web increased (Fig.~\ref{B}). For
    estuarine, lake, and stream food webs these decreases were more gradual towards the
    poles ($\beta_{Latitude}$=-0.007, $p$=0.006 for link density;
    $\beta_{Latitude}$=-0.009, $p$=0.002 for generality; and
    $\beta_{Latitude}$=-0.007, $p$=0.006 for vulnerability).
    In marine food webs there was very little effect of latitude on
    the strength of scaling ($\beta_{Latitude:Marine}$=0.009, $p$=0.047; 
    $\beta_{Latitude:Marine}$=0.011, $p$=0.028; 
    and $\beta_{Latitude:Marine}$=0.009, $p$=0.047 respectively),
    while in terrestrial food webs link density, generality, and vulnerability each
    decreased more gradually towards the 
    equator ($\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002; 
    $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; 
    and $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002).

    In contrast to the proportion of basal resources, link density, generality,
    and vulnerability tended to increase with increasing proportions of
    intermediate consumers (Fig.~\ref{I}; ). The best-fit models for scaling of link
    density and vulnerability with the proportion of intermediate consumers did
    not include any effect of latitude on scaling in any ecosystem type. Generality
    increased more rapidly towards the equator in estuarine, lake, marine, and
    stream food webs ($\beta_{Latitude}$=-0.006, $p$=0.009) and varied little with
    latitude in terrestrial food webs ($\beta_{Latitude:Terrestrial}$=0.008,
    $p$=0.053). In lake and stream food webs, generality increased more slowly
    with the proporiton of intermediate consumers such that, at low proportions,
    the effect of latitude could negate or reverse the increase.

    As with the proportion of basal resources; link density, generality, and
    vulnerability decreased as the proportion of top predators increased. For
    estuarine, lake, and marine food webs scaling of link density, generality, and
    vulnerability did not vary significantly with latitude
    ($\beta_{Latitude}$=-0.001, $p$=0.527 for link density;
    $\beta_{Latitude}$=-0.001, $p$=0.521 for vulnerability; the best-fit model for
    generality did not include any terms for latitude in any ecosystem type). In
    stream and terrestrial food webs, the decrease in link density and
    vulnerability was less sharp towards the poles, although this trend was
    significant only in streams ($\beta_{Latitude:Stream}$=0.015,
    $p$\textless0.001 and $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link
    density; $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
    $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability).

@@

  The tendency of food-web structure to exhibit scaling relationships with
  species richness has been well-established~\citep{Dunne2004,Riede2010}. As
  species richness in particular is also known to vary systematically over
  latitude~\citep{Schemske2009a,Macpherson2002,Kaufman1995}, intuitively one might suspect that any relationship
  between food-web properties such as generality might be due to the latitudinal
  gradient in species richness. In this dataset, however, we did not find
  overall latitudinal gradients in species richness, links per species, 
  generality, vulnerability, or the proportions of food webs accounted for by 
  basal resources, intermediate consumers, and top predators.

  The lack of a latitudinal gradient in species richness in this dataset contrasts
  strongly with other studies~\citep{Schemske2009a,Macpherson2002,Kaufman1995}. As numbers of species and links included in a food web
  vary strongly with sampling effort as well as with the underlying diversity of the study
  area, it is possible that the lack of latitudinal trends here is a result of researchers
  tending to expend similar amounts of sampling effort across studies. This could result in
  food webs describing species-rich tropical communities omitting more species and links
  than species-poor arctic communities. In addition, it is worth noting that gradients in
  species richness are generally measured for a single taxonomic group at a time (e.g.~\citep{Kaufman1995}).
  It is possible that these taxa are not well-represented in our food webs and that the
  dominant taxa in them do not have an underlying latitudinal gradient in richness. 
  In either case, the lack of a strong association between
  species richness and latitude in any ecosystem type
  means that any effect of latitude on other scaling 
  relationships is not being driven by an underlying 
  latitudinal gradient in species richness.
  The lack of confounding effects of latitude allows us to 
  more clearly assess effects of latitude on scaling with 
  species richness and proportions of species in different 
  trophic levels.

  Scaling of links per species, generality, and vulnerability with species
  richness varied strongly across ecosystem types. In estuarine, marine, and
  terrestrial food webs scaling of each property varied little with latitude.
  This is consistent with the idea that species' niche breadths do not vary
  systematically with temperature and productivity but that the niche space
  might be larger in species-rich communities~\citep{Davies2007}. Rather than
  niche space depending on temperature and productivity, it may be that species
  diversity itself affects the niche space available to species (although climate
  may affect speciation rates and therefore the diversity in a region~\citep{Currie2004}). 
  For example, as plant diversity increases both the 
  variety of food available to herbivores and the structural variety of the habitat will also increase.

  Unlike other ecosystem types, the scaling of generality
  in lake and stream food webs was stronger (i.e., 
  increased more steeply) in higher-latitude food webs. 
  In lake food webs, this trend was echoed in the scaling relationships
  between species richness and links per species and vulnerability.
  This means that species in tropical freshwater
  communities gain fewer additional feeding links per additional species in the
  web and that species in tropical lakes also gain fewer predators, and fewer links
  in general, per additional species. These trends are consistent with the hypothesis
  that greater stability in the tropics leads to narrower niches~\citep{Vazquez2004} and a higher proportion of
  specialists. This may be partly due to high-latitude species
  tending to switch between different seasonally-available
  prey~\citep{Isaac2012,Wilhelm1999} while tropical freshwater ecosystems may have more stable composition.

@@

%\end{spacing}
\newpage
\bibliographystyle{jae}%Compile with jae.bst style file
\bibliography{noISN}% your .bib file(s)

@@

\section*{Figures}

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/S_latlines_nonts.eps}
\caption{Scaling of link density, generality, and vulnerability with species richness
varies across ecosystem types and over latitude. For each property we show 
prediction curves for food webs at the equator (darkest line) and at 
20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
equator. We did not include direction (i.e., North or South) in our analyses. 
All curves are based on N=163 empirical food webs.}
\label{S}
\end{figure}

\begin{figure}[!H]
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/B_latlines_nonts.eps}
\caption{Scaling of link density, generality, and vulnerability 
with the proportion of basal resources in a food web
varies across ecosystem types and over latitude. For each property we show 
prediction curves for food webs at the equator (darkest line) and at 
20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
equator. We did not include direction (i.e., North or South) in our analyses. 
All curves are based on N=163 empirical food webs.}
\label{B}
\end{figure}

\begin{figure}[h]
\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/I_latlines_nonts.eps}
\caption{Scaling of link density, generality, and vulnerability 
with the proportion of intermediate consumers in a food web
varies across ecosystem types and over latitude. For each property we show 
prediction curves for food webs at the equator (darkest line) and at 
20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
equator. We did not include direction (i.e., North or South) in our analyses. 
All curves are based on N=163 empirical food webs.}
\label{I}
\end{figure}

>>>>

\vspace{-0.2 in}

@@

Several properties of food webs---the networks of feeding links between
species---vary systematically with the species richness of the underlying
community.  Under the ``latitude-niche breadth hypothesis'', which predicts
that species in the tropics will tend to evolve narrower niches, one might
expect that these scaling relationships could also be affected by latitude. To
test this hypothesis, we analysed the scaling relationships between species
richness and average generality, vulnerability, and links per species across a
set of 163 empirical food webs.  We also investigated scaling relationships
between the three food-web properties and the proportions of the web made up
by basal resources, intermediate consumers, and top predators. While we
observed no effect of latitude on scaling relationships with species richness
in the estuarine, marine, and terrestrial food webs, there were strong effects
of latitude on scaling relationships in the freshwater food webs. In these
communities, the latitude-niche breadth hypothesis appears to hold true while
in other habitat types niche breadth appears to vary little. These contrasting
findings indicate that it may be more important to account for habitat than
latitude when exploring gradients in food-web structure.

% \end{spacing}

@@

  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
  Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
  ecological communities~\citep{Petchey2008,Williams2000,Paine1966} and to understand how that structure relates to environmental variables 
  such as habitat type~\citep{Shurin2006,Briand1983}, primary productivity~\citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate~\citep{Baiser2012,Petchey2010}. The latter
  variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
  climate is more variable at high latitudes~\citep{Field1998}. These variables affect both the resources available and species' 
  metabolisms~\citep{Hechinger2011,White2011,OConnor2009,White2007}, and have been proposed as determinants of the strength of 
  interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
  By modulating interactions between species, latitudinal gradients may also shape food-web structure.
  Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
  latitudinal gradient in species richness, one of the most general and robust patterns in ecology~\citep{Schemske2009,Macpherson2002,Kaufman1995}.

@@

  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
  degree of specialization (i.e., the breadth of the Eltonian niche ~\citep{Elton1927}) of species within food webs.
  Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. 
  For example,
  narrower niches imply fewer links per species (i.e., greater specialization) in the tropics~\citep{Dyer2007,Marra1997}
  but see~\citep{Schleuning2012}). However,
  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialization may be obscured by a latitudinal gradient in species richness. If this is
  the case, it may still be possible to uncover effects of latitude on specialization by examining the shape of the scaling 
  relationship between specialization and species richness over changing latitude. Here, we use three measures of specialization:
  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
  latitude affects the scaling of each property with species richness, we test effects of latitude on specialization implied by
  the ``latitude-niche breadth hypothesis''.

@@

    We compiled a list of 163 empirical food webs from
    multiple sources (see \emph{Appendix S1} for web origins and selection
    criteria). We recorded study site latitude from the original source where
    possible or, where study sites were described but exact coordinates were not
    given, obtained estimated coordinates using Google Earth~\citep{GoogleEarth}.
    We then divided the species in each web into basal resources (those species with
    consumers but no prey), top predators (those species with prey but no predators),
    and intermediate consumers (species with both predators and prey, including cannibalistic
    species).

    As the food webs in this dataset are derived from a variety of sources and were compiled over many decades, it
    is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
    Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
    sets to form ``trophic species'' webs (e.g.~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}). As this study
    is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
    species with redundant sets of interactions. We therefore analysed both original and trophic-species versions
    of the dataset; in each case using the number of species and 
    links in each web to calculate the mean link density (number of links per species), mean generality 
    (number of prey per species), and mean vulnerability (number of predators per species) of the web. 
    The version of the dataset used did not qualitatively change the results, suggesting that
    the scaling relationships between species richness, other food-web properties, and latitude are very 
    similar whether or not redundant species are included. For simplicity, we present only
    the results for the original webs.

@@

    The scaling relationships between link density ($Z$) and species richness ($S$)
    has been shown to be a power law~\citep{Riede2010} of the form

@@

    \noindent As the two forms imply different error distributions, neither of which has strong
    \emph{a priori} justification in our dataset, we followed the recommendations in~\citet{Xiao2011}
    to compare the two model formulations explicitly (see \emph{Appendix S2} for details). 
    The logarithmic form (equation~\ref{Loglog}) provided the better fit to the data,
    as did the logarithmic forms of similar models for the scaling of generality and vulnerability. 
    We therefor used logarithmic models throughout the rest of the study.

@@

    After determining the appropriate form of the scaling relationship, we
    then assessed the impact of latitude on the scaling relationships between
    species richness and  link density, generality, vulnerability. In the
    context of the scaling relationships above, note  that this implies that
    we aim to determine the effect of latitude on the scaling exponent
    $\beta$. As when examining the relationships between latitude and each
    food  web property directly, we included a categorical variable for
    ecosystem type (stream, lake,  terrestrial, marine, or estuary), as well
    as interactions between food web type and latitude.

@@

  Link density, generality, and vulnerability each increased with increasing
  species richness (Fig~\ref{props_v_lat}; $\beta_0$=0.666,
  $p$\textless0.001; $\beta_0$=0.623, $p$\textless0.001; and
  $\beta_0$=0.666, $p$\textless0.001 respectively).  For estuarine, marine,
  and terrestrial food webs the strength of this scaling did not vary with
  latitude ($\beta_{Latitude}$=-0.001, $p$=0.267 for link density;
  $\beta_{Latitude}$=-0.001, $p$=0.363 for generality; and
  $\beta_{Latitude}$=-0.001, $p$=0.267 for vulnerability; Fig.~\ref{S}). In
  lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=0.005, $p$=0.008;
  $\beta_{Latitude:Lake}$=0.005, $p$=0.002; and
  $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively). In stream food
  webs generality increased more rapidly towards the poles
  ($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability
  did not vary with latitude.

  Unlike species richness, only generality increased with increasing
  proportions of basal resources in a web ($\beta_0$=-0.024, $p$=0.838;
  $\beta_0$=0.333, $p$=0.012; and $\beta_0$=-0.024, $p$=0.839 for link
  density, generality, and vulnerability respectively,
  Fig.~\ref{props_v_lat}). In each case, however, there were substantial
  effects of latitude on the scaling relationships. Thus, the scaling
  exponents for link density and vulnerability were negative for estaurine,
  lake, and stream communities and became more negative towards the poles
  ($\beta_{Latitude}$=-0.007, $p$=0.006 and $\beta_{Latitude}$=-0.007,
  $p$=0.006, respectively; Fig.~\ref{B}). For the scaling of link density and
  vulnerability in marine and terrestrial communities, the overall effect of
  latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.009,
  $p$=0.047; $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002 and
  $\beta_{Latitude:Marine}$=0.009, $p$=0.047;
  $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002, respectively) such that
  there was little overall scaling relationship. In contrast, the scaling
  exponent of generality with the proportion of basal resources was positive
  near the equator and negative near the poles in estuarine, lake, and stream
  communities ($\beta_{Latitude}$=-0.009, $p$=0.002) while the scaling
  exponents for marine and terrestrial communities were not significantly
  different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.028;
  $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; Fig.~\ref{B}).

  As with species richness, link density, generality, and vulnerability
  generally increased with the proportion of intermediate consumers in a web
  ($\beta_0$=1.74, $p$\textless0.001; $\beta_0$=1.92, $p$\textless0.001; and
  $\beta_0$=1.75, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}).
  The strength of this scaling decreased towards the poles in estuarine,
  lake, marine, and stream communities in each case
  ($\beta_{Latitude}$=-0.012, $p$=0.007; $\beta_{Latitude}$=-0.018,
  $p$\textless0.001; and $\beta_{Latitude}$=-0.012, $p$=0.007, respectively;
  Fig~\ref{I}). In terrestrial communities, however, scaling was stronger
  towards the  poles ($\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for
  link density; $\beta_{Latitude:Terrestrial}$=0.022, $p$=0.004 for
  generality; and $\beta_{Latitude:Terrestrial}$=0.016, $p$=0.022 for
  vulnerability, respectively).

  In contrast, link density, generality, and vulnerability decreased as the
  proportion of top predators increased ($\beta_0$=-0.511, $p$\textless0.001;
  $\beta_0$=-0.418, $p$\textless0.001; and $\beta_0$=-0.511, $p$\textless0.001
  respectively; Fig~\ref{props_v_lat}). For estuarine, lake, and marine
  food webs the strength of this scaling did not
  vary significantly with latitude ($\beta_{Latitude}$=-0.001, $p$=0.527 for
  link density; $\beta_{Latitude}$=-0.001, $p$=0.521 for vulnerability; the
  best-fit model for generality did not include any terms for latitude in
  any ecosystem type). In stream and terrestrial food webs, scaling was more
  strongly negative in the tropics and did not differ from zero near the poles,
  although this trend was only significant in streams
  ($\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link density;
  $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability; Fig~\ref{T}).

@@

  The tendency of food-web structure to exhibit scaling relationships with
  species richness has been well-established~\citep{Dunne2004,Riede2010}. As
  species richness in particular is also known to vary systematically over
  latitude~\citep{Schemske2009,Macpherson2002,Kaufman1995}, intuitively one
  might suspect that any relationship between food-web properties such as
  generality might be due to the latitudinal gradient in species richness. In
  this dataset, however, we did not find overall latitudinal gradients in
  species richness, links per species,  generality, vulnerability, or the
  proportions of food webs accounted for by  basal resources, intermediate
  consumers, and top predators (see \emph{Appendix S3} for details).

  The lack of a latitudinal gradient in species richness in this dataset contrasts
  strongly with other studies~\citep{Schemske2009,Macpherson2002,Kaufman1995}. As numbers of species and links included in a food web
  vary strongly with sampling effort as well as with the underlying diversity of the study
  area, it is possible that the lack of latitudinal trends here is a result of researchers
  tending to expend similar amounts of sampling effort across studies. This could result in
  food webs describing species-rich tropical communities omitting more species and links
  than species-poor arctic communities. In addition, it is worth noting that gradients in
  species richness are generally measured for a single taxonomic group at a time (e.g.~\citep{Kaufman1995}).
  It is possible that these taxa are not well-represented in our food webs and that the
  dominant taxa in them do not have an underlying latitudinal gradient in richness. 
  In either case, the lack of a strong association between
  species richness and latitude in any ecosystem type
  means that any effect of latitude on other scaling 
  relationships is not being driven by an underlying 
  latitudinal gradient in species richness.
  The lack of confounding effects of latitude allows us to 
  more clearly assess effects of latitude on scaling with 
  species richness and proportions of species in different 
  trophic levels.

  Scaling of links per species, generality, and vulnerability with species
  richness varied strongly across ecosystem types. In estuarine, marine, and
  terrestrial food webs scaling of each property varied little with latitude.
  This is consistent with the idea that species' niche breadths do not vary
  systematically with temperature and productivity but that the niche space
  might be larger in species-rich communities~\citep{Davies2007}. Rather than
  niche space depending on temperature and productivity, it may be that species
  diversity itself affects the niche space available to species (although climate
  may affect speciation rates and therefore the diversity in a region~\citep{Currie2004}). 
  For example, as the plant diversity of a community increases both the 
  variety of food available to herbivores and the structural variety of the habitat will also increase.

  Unlike other ecosystem types, the scaling of generality in lake and stream
  food webs was stronger (i.e.,generality increased more steeply with
  increasing species richness) in higher-latitude food webs.In lake food webs,
  this trend was echoed in the scaling relationships between species richness
  and links per species and vulnerability. This means that species in tropical
  freshwater communities gain fewer additional feeding links per additional
  species in the web and that species in tropical lakes also gain fewer
  predators, and fewer links in general, per additional species than species
  in high-latitude lakes. These trends are consistent with the hypothesis that
  greater stability in the tropics leads to narrower
  niches~\citep{Vazquez2004} and a higher proportion of specialists. This may
  be partly due to high-latitude species tending to switch between different
  seasonally-available prey~\citep{Isaac2012,Wilhelm1999} while tropical
  freshwater ecosystems may have more stable composition.

@@

\newpage
\bibliographystyle{jae}%Compile with jae.bst style file
\bibliography{noISN}% your .bib file(s)

\end{spacing}
\newpage

\section*{Figures}
\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
\caption{Scaling relationships for link density, generality (number of prey), 
and vulnerability (number of predators) 
against the proportions of basal resources (\% Basal), intermediate consumers (\% Intermediate), top 
predators (\% Top), and species richness of a food web. 
For each relationship, we show observed values corrected for
ecosystem type and latitude (grey circles), as well as the overall scaling relationship (N=163 food webs). For
the uncorrected values, see Fig.~\emph{S1}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

% \begin{figure}[H]
% \includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}
% \caption{Scaling relationships for link density, generality (number of prey), 
% and vulnerability (number of predators) against the proportions of basal resources (\% Basal),
% intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
% For each relationship, we show observed values (grey circles) and the scaling relationship, neglecting 
% any effects of habitat type or latitude (N=163 food webs). }
% \label{props_v_lat_obs}
% \end{figure}

% \newpage

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for species richness (black
line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{S}
\end{figure}

\begin{figure}[!H]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{B}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
intermediate consumers (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{I}
\end{figure}

\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
top predators (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{T}
\end{figure}
